Summary

### 2015-10-29 inst/examples/summary.Rmd
ok

[Discarded page count data](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages_discarded.csv)

[Successfully converted page counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages_accepted.csv)

@@

[Successfully converted publication places](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place.csv)

@@

[Accepted publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_accepted.csv)

[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.csv)

@@

[Accepted corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)

@@

[Accepted author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_accepted.csv)

[Discarded author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_discarded.csv)

@@

```{r topics2, echo=FALSE, message=FALSE, warning=FALSE}
# Write to file
f <- "output.tables/subjecttopics.tab"
print(paste("Complete subject topic counts in file:", f))
write.table(cbind(Topic = sort(names(tab))), file = f, sep = "\t", quote = F, row.names = F)
ntop <- 50
```

@@

>>>>

[Discarded page count data](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/pagecount_discarded.csv)

[Successfully converted page counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/pagecount_conversion.csv)

@@

[Successfully converted publication places](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place_accepted.csv)

@@

[Accepted publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_accepted.tab)

[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.tab)

@@

[Accepted corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_accepted.tab)

@@

[Accepted author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_accepted.tab)

[Discarded author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_discarded.tab)

@@

```{r topics2, echo=FALSE, message=FALSE, warning=FALSE}
# Write to file
f <- "output.tables/subjecttopics.tab"
write.table(cbind(Topic = sort(names(tab))), file = f, sep = "\t", quote = F, row.names = F)
ntop <- 50
```

[Complete subject topic counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/subjecttopics.tab)

@@

[Complete geoplace listing](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/geoplaces.csv)
